Appendix 1: sdmTMB statistical model description

### 2022-03-23 doc/appendix-model.Rmd
bold gamma_t

$$
\begin{aligned}
\mathbb{E}[y_{\s,t}] &= \mu_{\s,t},\\
\mu_{\bm{s},t} &=
f^{-1} \left( \bm{X}^{\mathrm{main}}_{\bm{s},t} \bm{\beta} +
O_{\s,t} +
\alpha_g +
\bm{X}^{\mathrm{tvc}}_{\bm{s},t} \gamma_t +
\bm{X}^{\mathrm{svc}}_{\bm{s},t} \zeta_{\bm{s}} +
\omega_{\s} +
\epsilon_{\s,t} \right),
\end{aligned}
$$

@@

$$
\begin{aligned}
  \mu_{\s,t} &= f^{-1} \left( \ldots +  \bm{X}^{\mathrm{tvc}}_{\s,t} \gamma_{t} + \ldots \right),\\
  \gamma_{t=1} &\sim \operatorname{Uniform} \left(-\infty, \infty \right),\\
  \gamma_{t>1} &\sim \operatorname{Normal} \left(\gamma_{t-1}, \sigma^2_{\gamma} \right),
\end{aligned}
$$

where $\gamma_t$ is an example optional time-varying regression parameter and $\bm{X}^{\mathrm{tvc}}_{\s,t}$ is the corresponding predictor value.
This is defined via the `time_varying` argument, assuming that the `time` argument is also supplied a column name.
For example, `time_varying ~ 0 + x`.
The first value is given an implicit uniform prior.
I.e., the same variable should not appear in the fixed effect formula since the initial value is estimated as part of the time-varying formula.
The formula `time_varying = ~ 1` implicitly represents a time-varying intercept and, this case, the intercept should be omitted from the main effects (`formula ~ + 0 + ...` or `formula ~ -1 + ...`).

@@

where $\boldsymbol{\zeta}$ is a random field representing a spatially varying coefficient.
Usually, $\bm{X}^{\mathrm{svc}}_{\s, t}$ would represent a predictor that is constant spatially for a given time $t$.
Currently, $\bm{X}^{\mathrm{svc}}_{t}$ is restricted to a single covariate (column vector), supplied by a one-sided formula to `spatial_varying`.
For example `spatial_varying = ~ 0 + x`, where `0` omits the intercept.

>>>>

$$
\begin{aligned}
\mathbb{E}[y_{\s,t}] &= \mu_{\s,t},\\
\mu_{\bm{s},t} &=
f^{-1} \left( \bm{X}^{\mathrm{main}}_{\bm{s},t} \bm{\beta} +
O_{\s,t} +
\alpha_g +
\bm{X}^{\mathrm{tvc}}_{\bm{s},t} \bm{\gamma_t} +
\bm{X}^{\mathrm{svc}}_{\bm{s},t} \zeta_{\bm{s}} +
\omega_{\s} +
\epsilon_{\s,t} \right),
\end{aligned}
$$

@@

$$
\begin{aligned}
  \mu_{\s,t} &= f^{-1} \left( \ldots +  \bm{X}^{\mathrm{tvc}}_{\s,t} \bm{\gamma_{t}} + \ldots \right),\\
  \gamma_{t=1} &\sim \operatorname{Uniform} \left(-\infty, \infty \right),\\
  \gamma_{t>1} &\sim \operatorname{Normal} \left(\gamma_{t-1}, \sigma^2_{\gamma} \right),
\end{aligned}
$$

where $\bm{\gamma_t}$ is an optional vector of time-varying regression parameters and $\bm{X}^{\mathrm{tvc}}_{\s,t}$ is the corresponding model matrix with covariate values.
This is defined via the `time_varying` argument, assuming that the `time` argument is also supplied a column name.
For example, `time_varying ~ 0 + x`.
The first value is given an implicit uniform prior.
I.e., the same variable should not appear in the fixed effect formula since the initial value is estimated as part of the time-varying formula.
The formula `time_varying = ~ 1` implicitly represents a time-varying intercept and, this case, the intercept should be omitted from the main effects (`formula ~ + 0 + ...` or `formula ~ -1 + ...`).

@@

where $\boldsymbol{\zeta}$ is a random field representing a spatially varying coefficient.
Usually, $\bm{X}^{\mathrm{svc}}_{\s, t}$ would represent a prediction matrix that is constant spatially for a given time $t$.
Currently, $\bm{X}^{\mathrm{svc}}_{t}$ is restricted to a single covariate (column vector), supplied by a one-sided formula to `spatial_varying`.
For example `spatial_varying = ~ 0 + x`, where `0` omits the intercept.
